---
title: "Behavioural Results KS-IC"
author: "J. Pablo Franco"
date: "`r format(Sys.time(), '%d %B, %Y')`"#"08/11/2017"
output: 
  html_document: 
    code_folding: hide
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
---

```{r doc_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>

```{r folder_management}
data_type="Work" #Directing to the right folder Raw Data or Work data
experiment="exp_v4"#"Exp" #e.g. "Pilot","Exp"
#versions=c("V2") #c("imV1")

#Folder Setup
if(dir.exists("~/Google Drive/My Drive")){
  mother_folder = "~/Google Drive/My Drive/"
} else {
  mother_folder = "~/Google Drive/"
}

project_folder = paste0(mother_folder,"Shared PabloDN/ICx3/")

code_folder = paste0(project_folder, "Code/behavAnalysis/")
data_folder = paste0(project_folder, "Data/Behavioural Data/", experiment,"/", data_type,"/")
setwd(code_folder)
knitr::opts_knit$set(root.dir = code_folder)

#Import functions
source(file.path(code_folder,"DescriptiveFunctions.R"))

# Participant Data
#fileParticipants = paste0(project_folder,"Data/Participants Log.csv")

# Task order Data 
# fileOrdertasks = paste0(project_folder,"Data/Behavioural Data/", experiment,"/Taskorder.csv")
#666

#3SAT Data Text files
folderDataSAT=paste0(data_folder,"SAT/")

# TSP Data Text files
folderDataTSP=paste0(data_folder,"TSP/")


folderOut_figures = paste0(code_folder,"Output/Figures")
folderOut_tables = paste0(code_folder,"Output/Tables")

#Solver Data Text files


# SAT Files
folderIn_solver_SAT = paste0(mother_folder,"Melbourne/UNIMELB/Research/Complexity Project/Simulations Data/3-SAT/sat-results/")
fileIn_solverP_SAT = paste0(folderIn_solver_SAT,"kd-5p/minisat_sat_5p_results.csv")
fileIn_solverE_SAT = paste0(folderIn_solver_SAT,"kd-5e/minisat_sat_5e_results.csv")

#TSP Files
folderIn_solver_TSP =paste0(mother_folder,"Melbourne/UNIMELB/Research/Complexity Project/Simulations Data/TSP/exp-20-5/")

fileIn_solver_TSP = paste0(folderIn_solver_TSP,"tsp-20-5.csv")

# folderInstanceInfo='~/Google Drive/Melbourne/UNIMELB/Research/Complexity Project/Simulations Data/'
# fileDecInstances = paste0(folderInstanceInfo,'KS decision/decisionInstancesInfoSubset.csv')
# fileOptInstances = paste0(folderInstanceInfo,'KS optimisation/optimisationInstancesInfoSubset.csv')
# 
# fileDecInstancesAll = paste0(folderInstanceInfo,'KS decision/decisionInstancesInfo.csv')
# 
# optTaskMaxTime=60

SATTaskMaxTime=110
nVars_sat=5

TSPTaskMaxTime = 40



```

```{r setup, collapse=TRUE}
## Setting up the basics
library(ggplot2)
library(lme4)
library(stargazer)
library(knitr)
library(dplyr)
library(ggsignif)
library(pander)
library(plotly)
library(reshape2)
library(Hmisc)
library(readr)

#library(tibble)
#library(plotrix)

#Stores a list of all the regressions that are run
#allModels=vector("list", length=0)

#Output type for tables. Use "html" to view the output .html file and use "latex" to export .tex tables
#outputType="html"

```

# 3-SAT

## Import SAT data and omit invalid responses
```{r sat_Import}
#KS Import 
dataTrial_SAT = importTrialInfo(folderDataSAT)

#Adds Phase Transition Dummy Variable to data (1-> in Phase Transition / 0 -> Out of Phase Transition)
dataTrial_SAT$phaseT=as.numeric(dataTrial_SAT$type<=4)

#Filter additional participants.
participantsToOmit=c("sat01","sat15")
dataTrial_SAT = dataTrial_SAT %>% filter(!(pID %in% participantsToOmit))

print(paste0(length(participantsToOmit)," participants were omitted in the analysis. sat15 always answered yes. sat01 answered YES most of the time, and on the 3 he answered NO, only 1 was correct."))


# Cleaning Decsion Data:
# Filters out those trials in which an answer was not given or an error acurred
nOmitTrials = length(dataTrial_SAT$answer[dataTrial_SAT$answer>=2])
NOmitPart= length(unique(dataTrial_SAT$pID[dataTrial_SAT$answer>=2]))
dataTrial_SAT=dataTrial_SAT %>% filter(answer<2)
print(paste(nOmitTrials,"Trials were omitted due to non-answers (from", NOmitPart,"Participants)."))


#Add a "region" column
dataTrial_SAT = dataTrial_SAT %>% mutate(region=recode(type, `1`= 'Phase Transition', `2`= 'Phase Transition', `3`= 'Phase Transition', `4`='Phase Transition', '5'='Overconstrained', '6'='Underconstrained'))

```


## Omit invalid response times
```{r}

### Time Spent Data Cleaning

# Omit those participants that never submitted their answer from the timeSpent analysis
#omitPID = c("be19","be31")
minTimeSpent = dataTrial_SAT %>% group_by(pID) %>% summarise(minTime = min(timeSpent)) 
omitPID = minTimeSpent$pID[abs(SATTaskMaxTime-minTimeSpent$minTime)<0.1] #Select those participants whose min time spent was optTaskMaxTime
dataTrial_SAT_Time=dataTrial_SAT[!(dataTrial_SAT$pID %in% omitPID),]
print(paste0("For time analysis (*effort*) ", length(omitPID)," participants that never submitted their answers were omitted."))

#Omit Participant that in the first block didn't know they could skip
dataTrial_SAT_Time=dataTrial_SAT_Time %>% filter(!(pID=="ic11" & block==1))
print(paste0("For time analysis (*effort*) block 1 of an additional Participant was omitted because they didn't understand they could skip (based on what participant said druing experiment)"))


```

## Import solver data
```{r}
#Import simulations data (e.g. propagations data)

simulationsData1= read.csv(fileIn_solverP_SAT,stringsAsFactors = FALSE)
simulationsData2= read.csv(fileIn_solverE_SAT,stringsAsFactors = FALSE)
simulationsData_SAT=bind_rows(simulationsData1,simulationsData2)

simulationsData_SAT = dplyr::rename(simulationsData_SAT,id=case_id)

dataTrial_SAT_sims =inner_join(dataTrial_SAT,simulationsData_SAT, by=c("id","ratio"))

dataTrial_SAT_sims_Time =inner_join(dataTrial_SAT_Time,simulationsData_SAT, by=c("id","ratio"))

```

## Import click data
```{r}
dataclicks_SAT = importTrialInfo_clicks(folderDataSAT)
```


## Save Clean Data to file
```{r}

write_csv2(dataTrial_SAT_sims,file.path(data_folder,"SAT_clean.csv"))

write_csv2(dataTrial_SAT_sims_Time,file.path(data_folder,"SAT_clean_time.csv"))

write_csv2(dataclicks_SAT,file.path(data_folder,"SAT_clicks.csv"))

```

# TSP

## Import TSP data and omit invalid answers
```{r tsp_Import}
#TSPImport 
dataTrial_TSP = importTrialInfo(folderDataTSP)

#Adds Phase Transition Dummy Variable to data (1-> in Phase Transition / 0 -> Out of Phase Transition)
dataTrial_TSP$phaseT=as.numeric(dataTrial_TSP$type<=4)

#Filter participants.
participantsToOmit=c("tsp19")
dataTrial_TSP = dataTrial_TSP %>% filter(!(pID %in% participantsToOmit))
print(paste0(length(participantsToOmit)," participant was omitted in the decision analysis. tsp19 didn't understand the instructions concerning submission of the answer. Experimenter talked to him, and he clearly didn't understand the purpose of the YES/NO buttons."))

# Cleaning Decsion Data:
# Filters out those trials in which an answer was not given
nOmitTrials = length(dataTrial_TSP$answer[dataTrial_TSP$answer>=2])
NOmitPart= length(unique(dataTrial_TSP$pID[dataTrial_TSP$answer>=2]))
dataTrial_TSP=dataTrial_TSP %>% filter(answer<2)
print(paste(nOmitTrials,"Trials were omitted due to non-answers (from", NOmitPart,"Participants)."))

#Add a "region" column
dataTrial_TSP = dataTrial_TSP %>% mutate(region=recode(type, `1`= 'Phase Transition', `2`= 'Phase Transition', `3`= 'Phase Transition', `4`='Phase Transition', '5'='Overconstrained', '6'='Underconstrained'))


```


## Omit invalid response times 
```{r}
# Omit those participants that never submitted their answer from the timeSpent analysis
#omitPID = c("be19","be31")
minTimeSpent = dataTrial_TSP %>% group_by(pID) %>% summarise(minTime = min(timeSpent)) 
omitPID = minTimeSpent$pID[abs(TSPTaskMaxTime-minTimeSpent$minTime)<0.1] #Select those participants whose min time spent was optTaskMaxTime
dataTrial_TSP_Time=dataTrial_TSP[!(dataTrial_TSP$pID %in% omitPID),]
print(paste0("For time analysis (*effort*) ", length(omitPID)," participants that never submitted their answers were omitted."))
```

## Import solver data
Propagations and accuracy by Instance
```{r}
#Import simlations data (e.g. propagations data)

simulationsData_TSP= read.csv(fileIn_solver_TSP,stringsAsFactors = FALSE)

simulationsData_TSP = dplyr::rename(simulationsData_TSP,id=problem)

extract_id_TSP = function(path_string){
  path = strsplit(path_string,"/")[[1]]
  file = path[length(path)]
  id = sub(".dzn","",file)
}

#Accuracy dataset with solver information (propagations)
dataInput = dataTrial_TSP
dataInput$id = sapply(dataInput$id,extract_id_TSP)
dataTrial_TSP_sims =inner_join(dataInput,simulationsData_TSP, by="id")
dim(dataTrial_TSP_sims)

#Time dataset with solver information (propagations)
dataInput = dataTrial_TSP_Time
dataInput$id = sapply(dataInput$id,extract_id_TSP)
dataTrial_TSP_sims_Time =inner_join(dataInput,simulationsData_TSP, by="id")
dim(dataTrial_TSP_sims_Time)


```

## Import click data
```{r}
dataclicks_TSP = importTrialInfo_clicks(folderDataTSP)##TODO
```

## Save Clean Data to file
```{r}

write_csv2(dataTrial_TSP_sims,file.path(data_folder,"TSP_clean.csv"))

write_csv2(dataTrial_TSP_sims_Time,file.path(data_folder,"TSP_clean_time.csv"))

write_csv2(dataclicks_TSP,file.path(data_folder,"TSP_clicks.csv"))

```



